Twisted 11-dimensional supergravity, I

### 2021-08-10 draft.tex
merge
dimensional reduction modulo proof

\subsection{Superconformal algebras}

@@

\begin{prop}
The $Q$-twist of the 6d $\cN=(2,0)$ superconformal algebra is $\lie{osp}(6|1)$. 
\end{prop}

@@

\begin{itemize}
\item
The even part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
\[
\lie{sl}(4) \oplus \lie{sl}(2)
\]
which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.

@@

The odd part of $\lie{osp}(6|1)$ is 
\[
\wedge^2 \CC^4 \otimes \CC^2 
\]
which we can write as $\wedge^2 W \otimes R$. 
Let us further split $W = L \oplus \CC$, with $L = \CC^3$ the fundamental $\lie{sl}(3)$ representation. 
Then the odd part decomposes as
\[
\wedge L \otimes R \oplus \wedge^2 L \otimes R .
\]

\begin{itemize} 
\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
It is mapped to the fields 
\[
z_i \d w_a \in \Omega^{1,0}(\CC^3) .
\] 
\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
It is mapped to the fields
\[
\ep_{ij} z_i w_a \d z_j \in \Omega^{1,0}(\CC^3) , \quad a = 1,2, \quad i,j = 1,2,3. 
\]
\end{itemize}

%6d suco 
%what about 3d N=8 suco?

@@

\section{The twisted $\Omega$-backround}

@@

>>>>

\subsection{Supersymmetric indices}

\brian{SU(5) and SU(2) character calculations}

\subsection{6d superconformal algebra and the M5 brane}

@@

\begin{prop}
The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
\end{prop}

@@

The even part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
\[
\lie{sl}(4) \oplus \lie{sl}(2)
\]
which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.

\begin{itemize}

@@

The odd part of $\lie{osp}(6|1)$ is 
\[
\wedge^2 \CC^4 \otimes \CC^2 
\]
which we can write as $\wedge^2 W \otimes R$. 
Let us further split $W = L \oplus \CC$, with $L = \CC^3$ the fundamental $\lie{sl}(3)$ representation. 
Then the odd part decomposes as
\[
L \otimes R \oplus \wedge^2 L \otimes R .
\]

\begin{itemize} 
\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
It is mapped to the fields 
\[
z_i \d w_a \in \Omega^{1,0}(\CC^3),\quad a=1,2, \quad i =1,2,3.
\] 
\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
It is mapped to the fields
\[
\ep_{ij} z_i w_a \d z_j \in \Omega^{1,0}(\CC^3) , \quad a = 1,2, \quad i,j = 1,2,3. 
\]
\end{itemize}

\subsection{3d superconformal algebra and the M2 brane}

%what about 3d N=8 suco?

@@

\section{The twisted $\Omega$-background}

@@

\section{BCOV stuff}
